---
title: "hw7"
author: "Jin Chen"
date: "3/2/2020"
output: html_document
---

**Question 2:**

Comment the image.directory.df function.

**Code given**

```{r, include = FALSE}
# Load required libraries
library("imager") # For reading in images, manipulating them in R, and display
library("plyr")   # More uniform and flexible successors to apply, lapply, etc.
```

```{r}
common.width <- 350
common.height <- 450
```

```{r}
# Flatten an image into a vector
# Input: an image (img)
# Output: a numerical vector
# Presumes: img is in the "cimg" format used by the imager library
image.to.vector <- function(img) {
    # Note: the cimg format extends higher-dimensional numerical arrays,
    # so converting them to long vectors is easy in this case,
    # but other data structures are more complicated, and this doesn't hurt
    as.vector(img)
}

```

```{r}
# Load all image, resize them, flatten them into vectors, and combine them into a data frame
# Input: all the image files(.jpg) in a directory
# Output: a data frame containing all the numerical vectors
image.directory.df <- function(path=".",
                            pattern="*.jpg",
                            width=common.width,
                            height=common.height) {
    require("imager")
    require("plyr")
    # List of all the image file names in a directory
    image.filenames <- dir(path=path, pattern=pattern, full.names=TRUE)
    # Load the images and store them in a list
    images.list <- llply(.data=image.filenames, .fun=load.image)
    # Resize the images to 350*450
    images.resized <- llply(.data=images.list, .fun=resize,
                             size_x=width, size_y=height)
    # Flatten the images into vectors and combining them in a data frame
    images.df <- ldply(.data=images.resized, .fun=image.to.vector)
    return(images.df)
}
```

```{r}
# Convert a vector into an image
# Inputs: vector of numbers (vec)
  # width of desired image (width, default common.width)
  # height of desired image (height, default common.height)
# Output: an image in cimg format as used by the imager library
# Presumes: vec is numeric
  # vec has width*height*3 entries (3 for color)
vector.to.image <- function(vec, width=common.width, height=common.height) {
    require("imager")
    # Make sure input is boiled down to a numeric vector
    vec <- as.numeric(vec)
    # cimg format has 4 dimensions: width, height, time or depth, colors
    # setting 3rd dimension to have length 1 forces this to be a still 2D
    # image
    shaped <- array(vec, dim=c(width, height, 1, 3))
    as.cimg(shaped)
}
```

**Question 3:**

Use the image.directory.df function to create a data frame storing all of the re-sized images. (You will have to change at least one of the default settings.) Give the dimensions of the data frame. Explain why it has that number of columns and that number of rows. (You may need to look carefully at the code.) 

```{r}
df <- ima
```


